Dynamic Witnesses for Static Type Errors

### 2015-11-20 paper/pldi16-submission/evaluation.tex
misc edits
fix RJ comment

\paragraph{Jump Compression}
%
A jump compressed trace is one whose edges are limited to forward
or backward jumps. (The sizes of these traces is equal to the jump
metric above.)
%
In our experience, jump compression abstracts many details of the
computation that are often uninteresting or irrelevant to the
explanation, or at any rate, easily summarized as call-return
pairs.
%
Note that jump compressed traces are not quite the same as
stack-traces as they show \emph{all} function calls, including
those that returned successfully.
%
For example, the display on the right in Figure shows
a jump-compressed trace, of size 4. The full trace for
the same example has size \RJ{Eric please fix this...}

\paragraph{Metrics} Thus, our two metrics are:
% size of the full trace,
% \ie the number of small-step reductions, and the size of the jump-compressed
% version of the trace.
%
\begin{enumerate}
\item \emphbf{Single-Step Metric}
      The number of single-step reductions along the path from the
      witness to the stuck term in the given witness execution, and
  % This can be thought of as a worst-case
  % complexity, \ie ``How big is the fully-expanded trace?''
\item \emphbf{Jump Metric}
      The size of the jump-compressed trace for the given witness execution,
      \ie\ the number forward (or backward) jumps that can be taken along the
      path from the witness to the stuck term.
\end{enumerate}

@@

\paragraph{Results}
\label{sec:results-complexity}
The results of the experiment are summarized in
Figure~\ref{fig:results-complexity}.
%
The average number of single-step reductions per trace is 26 for our
dataset (27 for the \uwbench\ dataset) with a maximum of 2,744 (659 for
\uwbench). The average number of jumps per trace is 3 (also 3 for
\uwbench) with a maximium of 177 (52 for \uwbench). In both datasets at
least 90\% of the traces contain fewer than 10 jumps.
%

@@

>>>>

\paragraph{Jump Compression}
%
A jump compressed trace is one whose edges are limited to forward
or backward jumps. (The sizes of these traces is equal to the jump
metric below.)
%
In our experience, jump compression abstracts many details of the
computation that are often uninteresting or irrelevant to the
explanation, or at any rate, easily summarized as call-return
pairs.
%
Note that jump compressed traces are not quite the same as
stack-traces as they show \emph{all} function calls, including
those that returned successfully.
%
For example, the display on the right in Figure~\ref{fig:factorial} shows
a jump-compressed trace, of size 4. The full trace for
the same example has size 19.

\paragraph{Metrics} Thus, our two metrics are:
% size of the full trace,
% \ie the number of small-step reductions, and the size of the jump-compressed
% version of the trace.
%
\begin{enumerate}
\item \emphbf{Single-Step Metric}
      The number of single-step reductions along the path from the
      witness to the stuck term in the given witness execution, and
  % This can be thought of as a worst-case
  % complexity, \ie ``How big is the fully-expanded trace?''
\item \emphbf{Jump Metric}
      The size of the jump-compressed trace for the given witness execution,
      \ie\ the number of forward (or backward) jumps that can be taken along the
      path from the witness to the stuck term.
\end{enumerate}

@@

\paragraph{Results}
\label{sec:results-complexity}
The results of the experiment are summarized in
Figure~\ref{fig:results-complexity}.
%
The average number of single-step reductions per trace is 26 for the \ucsdbench\
dataset (27 for the \uwbench\ dataset) with a maximum of 2,744 (659 for
\uwbench). The average number of jumps per trace is 3 (also 3 for
\uwbench) with a maximium of 177 (52 for \uwbench). In both datasets at
least 90\% of the traces contain fewer than 10 jumps.
%

@@

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "main"
%%% End:
